---
title: "02 CSI online aphasia: Spoken - Preprocessing Final Data Set"
author: "Kirsten Stark"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Load packages

```{r load_packages, message=FALSE}
rm(list = ls())

# install.packages("remotes") # uncomment if installation is needed (only once)
# remotes::install_github("rstudio/renv") # uncomment if installation is needed (only once)
# if file is accessed through the R package, all packages should be installed if 
# renv::restore()
# is applied. Otherwise use: 
# install.packages("tidyr") # uncomment if installation is needed (only once)
# install.packages("dplyr") # uncomment if installation is needed (only once)
# install.packages("here") # uncomment if installation is needed (only once)
# install.packages("knitr")

library(tidyr)
library(dplyr)

options( "encoding" = "UTF-8" )
```


# Load and preprocess data
This input file needs to be entered by hand: 

```{r specify input}
# input output main data
type <- c("PWA", "control")

## Load files from the control and the PWA group
for(i in 1:length(type)){
  # read in file names
  eval(parse(text=paste0("files_", type[i], 
         "<- list.files(here::here('data', 'raw', 'final','",type[i], 
         "'), recursive = TRUE)")))
  ## sosci_files
  eval(parse(text=paste0("sosci_files_", type[i], 
                         "<- files_", type[i], 
                         "[grep('data.csv', files_", type[i],",
                         fixed=T)]")))
  ## vot files
  eval(parse(text=paste0("vot_files_", type[i], 
  "<- files_", type[i], 
  "[-grep('data.csv', files_", type[i],", fixed=T)]")))
}
```


```{r load_additional files}
# output file name 
output <- c("aphasia_final.csv")

# arrays
arrays <- "arrays_umlaut.csv" # experimental arrays
```

```{r load_data, warning=FALSE}
for(i in 1:length(type)){
  ##### SOSCI FILES
  # reorder sosci files
  eval(parse(text=paste0(
    "sosci_files_", type[i], 
    "<- c(sosci_files_", type[i], "[substr(sosci_files_", type[i],
    ", 2,2)=='.'] %>% sort(),",  
    "sosci_files_", type[i], "[substr(sosci_files_", type[i],
    ", 2,2)!='.'] %>% sort())")))
  
  # load sosci file data
  eval(parse(text=paste0("datafiles_", type[i], "<- list()")))
  eval(parse(text=paste0("for(j in 1:length(sosci_files_", type[i],")) {",
        "datafiles_", type[i], "[[j]] <- 
        read.csv(here::here('data', 'raw', 'final','", type[i], "',
        sosci_files_", type[i], "[j]), sep = ';', na = '')",
        "}"))) 
  
  # save cell instructions
  if(i == 1){
      eval(parse(text=paste0("instructions <- datafiles_",
                             type[i],"[[1]][1,]")))
  }
  
  # perform some transformations on each data frame
  eval(parse(text=paste0("for(j in 1:length(sosci_files_",type[i],")){",
    # add original name
    "datafiles_", type[i], "[[j]]$name","<- sosci_files_",type[i],"[j];",

    # add type column
    "datafiles_", type[i], "[[j]]$type","<- '",type[i], "';",

    # delete instruction column
    "if(datafiles_", type[i], "[[j]][1,1] ==",
    "'Interview-Nummer (fortlaufend)') {",
          "datafiles_", type[i], "[[j]] <-",
          "datafiles_", type[i], "[[j]][-c(1),]",
    "};",

    # add subject id: each subject is saved in a separate folder
      "datafiles_", type[i], "[[j]]$subject <- i*100+j;",
    
    # add testing session per subject
    "datafiles_", type[i], "[[j]] <-","datafiles_", type[i], "[[j]] %>% ",
                           "dplyr::mutate(session = row_number())",

    "}")))
  
  
    ##### VOT FILES
  # reorder VOT Data
  eval(parse(text=paste0("vot_files_", type[i], "<- 
    c(vot_files_", type[i], "[substr(vot_files_", type[i],", 2,2)==
    '.'] %>% sort(),
    vot_files_", type[i], "[substr(vot_files_", type[i], ",2,2)!=
    '.'] %>% sort())"))) 
  
  
  # load VOT DATA
  eval(parse(text=paste0("datafiles_vot_", type[i], "<- list()")))
  eval(parse(text=paste0("for(j in 1:length(vot_files_",type[i], ")) {",
     "datafiles_vot_", type[i], "[[j]] <- ",
     "read.csv(here::here('data', 'raw', 'final', '", type[i], "',
     vot_files_", type[i], "[j]), sep =',', na = '');",
     "datafiles_vot_", type[i], "[[j]]$name <- vot_files_", type[i], "[j];",
  "}"))) 
  
  
  # perform some transformations on each dataframe
  participant <- 1
  
  eval(parse(text=paste0("for(j in 1:length(vot_files_", type[i], ")) {",
                         
    # # add original name
    # "datafiles_vot_", type[i], "[[j]]$name_vot <- 
    # vot_files_", type[i], "[j];",
    
    # add type column
    "datafiles_vot_", type[i], "[[j]]$type <- '", type[i], "';",
    "}")))
    
    # add subject personal code 
  eval(parse(text=paste0("for(j in 1:length(vot_files_", type[i], ")) {",
    "if(substr(vot_files_", type[i],", 2,2)=='.'){",
      "datafiles_vot_", type[i], "[[j]]$OR02_01 <-",
        "substr(vot_files_", type[i],"[j], 4,9)",
    "} else {",
      "datafiles_vot_", type[i], "[[j]]$OR02_01 <- ",
        "substr(vot_files_", type[i], "[j], 5,10)",
    "};",
    
    # add subject id: each subject is saved in a separate folder
    "if (j == 1) {",
      "datafiles_vot_", type[i], "[[j]] <- datafiles_vot_", type[i],
        "[[j]] %>% dplyr::mutate(subject = participant)",
    "} else if (datafiles_vot_", type[i], "[[j]]$OR02_01[1] ==",
                "datafiles_vot_", type[i], "[[j-1]]$OR02_01[1]){",
        "datafiles_vot_", type[i], "[[j]] <- datafiles_vot_", type[i], 
        "[[j]] %>% dplyr::mutate(subject = participant);",
    "} else if (datafiles_vot_", type[i], "[[j]]$OR02_01[1] !=",
                "datafiles_vot_", type[i], "[[j-1]]$OR02_01[1]){",
        "participant <- participant +1;",
         "datafiles_vot_", type[i], "[[j]] <-",
           "datafiles_vot_", type[i], "[[j]] %>%",
           "dplyr::mutate(subject = participant)",
    "} else {",
       "print('error')",
    "};", 
    
    "datafiles_vot_", type[i], "[[j]] <- 
    datafiles_vot_", type[i], "[[j]]", "%>% ",
                           "dplyr::mutate(subject =", i*100, "+
                           datafiles_vot_", type[i], "[[j]]$subject);",

  
    #   # add session ID
    "datafiles_vot_", type[i], "[[j]] <- datafiles_vot_", type[i],
    "[[j]] %>%
      mutate(session=stringr::str_sub(name, start = -16)) %>%
      mutate(session=stringr::str_sub(session, start = 1, end=1)) %>%
      mutate(session=as.numeric(as.character(session)));",

    # fix corrupted trial no
    "colnames(datafiles_vot_", type[i], "[[j]])[1] <- 'trial';",
  "}")))
  }
  
# bind sosci-files together
datafiles <- c(datafiles_PWA, datafiles_control)
  
# bind vot-files together
datafiles_vot <- c(datafiles_vot_PWA, datafiles_vot_control)

## fix single column names
for(i in 1:(length(vot_files_PWA)+length(vot_files_control))){
  if("error......" %in% colnames(datafiles_vot[[i]])){
    datafiles_vot[[i]] <-  datafiles_vot[[i]] %>% rename(error=error......)
  }
}
```

# Convert to long format, prepare wide dataframe, and bind long and wide dataframes together
First convert all variables with values for each trial, then bind them together. In a next step bind them to the variables that only have one value per participant.

```{r prepare_long_df}
for(i in 1:(length(sosci_files_PWA)+length(sosci_files_control))){
  # print(i)
#-------------------------------------------------------------
# Prepare long data frame
      ### AUDIO FILES
      # In some of the data files, two columns seem to be missing and the order of the columns is corrupted - adjust this ( in the TeaP data only row 3 of participant1)
      for (j in nrow(datafiles[[i]])) {
        if (!grepl("AR01", datafiles[[i]]$AR01x02[j], fixed=TRUE)) {
          for (k in 407:20){
            datafiles[[i]][j,k] <- datafiles[[i]][j, k-1]
          }
          for (k in 407:38){
            datafiles[[i]][j,k] <- datafiles[[i]][j, k-1]
          }
        }
      }
      
      # Rename session like the audio files 
      datafiles[[i]]$session <- 
        stringr::str_sub(datafiles[[i]]$AR01x02, start = -11)
      
      # Audio files of first 1-80 trials
      df1 <- datafiles[[i]] %>% 
              select('subject', starts_with("AR")&contains("x")) %>% 
                      pivot_longer(
                        cols = -subject,
                         names_to = c("trial"), 
                        values_to = "audio") %>%
                        group_by(subject) 
                        # order by AR, but for each repetition separately
      df1$session <- stringr::str_sub(df1$audio, start = -11)
      df1 %>% 
        arrange(session, trial) %>% 
        mutate(trial = 
                 as.numeric(as.character(stringr::str_sub(trial, 3,4))))-> df1
    
      # Audio files of last 1-80 trials
      df2 <- datafiles[[i]] %>% 
              select('subject', starts_with("AU")&contains("x")) %>% 
                      pivot_longer(
                        cols = -subject,
                         names_to = c("trial"), 
                        values_to = "audio") %>%
                        group_by(subject) 
                        # order by AU, but for each repetition separately
      df2$session <- stringr::str_sub(df2$audio, start = -11)
      df2 %>%
        arrange(session, trial) %>%
        mutate(trial = 
                 as.numeric(as.character(
                   stringr::str_sub(trial, 3,4)))+80)-> df2
      
      # bind first 80 and last 80 trials together
      df_audio <- bind_rows(df1, df2) %>%
            arrange(subject, session, trial)
      
      if(nrow(df_audio) != 480) { 
        print('error - audio files dont have correct length')}
      
      # delete audio file columns from wide data frame
      datafiles[[i]] <- datafiles[[i]] %>% 
          select(!starts_with(c("AR", "AU")))
      
      ### Arrange order
     df_main <- df_audio %>% arrange(subject, session, trial)
     
     
     #-------------------------------------------------------------
  # Adapt wide data frame with info that is assessed only once
  
  # for control reasons: calculate time sum by hand:
  # sum dwell times for each page
  datafiles[[i]] <- datafiles[[i]] %>% 
    mutate_at(vars(contains("TIME0")), as.numeric)
  datafiles[[i]] <- datafiles[[i]] %>% rowwise() %>% 
    dplyr::mutate(timetotal = rowSums(across(starts_with("TIME0")),
                                      na.rm=TRUE)/60)
  # delete columns with info we don't need
  if("SD22_BVS" %in% colnames(datafiles[[i]])){
    datafiles[[i]] <- datafiles[[i]] %>% 
    select(-c(SERIAL, REF, MODE, SD22_PRV,SD22_BVS,LASTDATA, 
              SD19, SD19_01, SD19_02, SD19_03, MISSING, MISSREL))
  } else {
    datafiles[[i]] <- datafiles[[i]] %>% 
    select(-c(SERIAL, REF, MODE, SD22_PRV,LASTDATA, 
              SD19, SD19_01, SD19_02, SD19_03, MISSING, MISSREL))
}

# delete columns that contain only NAs
datafiles[[i]]<- datafiles[[i]] %>% select_if(~sum(!is.na(.)) > 0)

# delete practice audio files
  datafiles[[i]]<- datafiles[[i]] %>% select(!starts_with("PA"))

# add comments column if participant left no comment
if(!("IM01_01" %in% colnames(datafiles[[i]]))){
  datafiles[[i]]$IM01_01 <- ""
}

# give columns more recognizable names
  datafiles[[i]] <- datafiles[[i]] %>% 
  dplyr::rename(gender = SD01, age = SD02_01,language = SD21, 
                     os_system = SD22_OS, browser_automatic = SD22_BNM,
                     system_format  = SD22_FmF,
                     handedness = SD27, 
                     comments = IM01_01, time_wo_outlier = TIME_SUM,
                     screen_width = SD22_ScW, screen_height = SD22_ScH,
                     questionnaire_width = SD22_QnW)


#-------------------------------------------------------------
# Bind long and wide data frame together
# Repeat each subjects' rows 160 times (no of trials)
datafiles[[i]] <- datafiles[[i]] %>% slice(rep(seq_len(n()), 160))

# Add trial number to wide data frame
datafiles[[i]]$trial <- 
  rep(1:160, times = length(unique(datafiles[[i]]$session)))

# Arrange by session and trial
datafiles[[i]] %>% arrange(subject, session, trial) -> datafiles[[i]]

# bind wide and long info together
datafiles[[i]] <- datafiles[[i]] %>% 
  left_join(df_main, by = c("subject", "session", "trial")) %>%
  relocate(subject, session, trial)

# make sure sessions are ordered in the correct order: 
datafiles[[i]] %>% arrange(STARTED) -> datafiles[[i]]

# rename sessions in numerical order
datafiles[[i]] %>% mutate(session=case_when(
  STARTED == unique(datafiles[[i]]$STARTED)[1] ~ 1,
  STARTED == unique(datafiles[[i]]$STARTED)[2] ~ 2,  
  STARTED == unique(datafiles[[i]]$STARTED)[3] ~ 3))-> datafiles[[i]]

# prepare for merging
datafiles[[i]] <- datafiles[[i]] %>% select(-CASE)
datafiles[[i]] <- datafiles[[i]] %>% 
 #  mutate(CASE = as.character(CASE))%>% 
   mutate(OR01_01 = as.numeric(as.character(OR01_01))) %>% 
   mutate(gender = as.numeric(as.character(gender))) %>% 
   mutate(age = as.numeric(as.character(age))) %>% 
  mutate(language = as.numeric(as.character(language))) %>% 
  mutate(os_system = as.numeric(as.character(os_system))) %>% 
  mutate(system_format = as.numeric(as.character(system_format))) %>% 
  mutate(handedness = as.numeric(as.character(handedness))) %>% 
  mutate(comments = as.character(comments)) %>% 
  mutate(time_wo_outlier = as.numeric(as.character(time_wo_outlier))) %>% 
  mutate(screen_width = as.numeric(as.character(screen_width))) %>%
  mutate(screen_height = as.numeric(as.character(screen_height))) %>% 
  mutate(questionnaire_width = as.numeric(as.character(questionnaire_width)))%>% 
  mutate(browser_automatic = as.numeric(as.character(browser_automatic))) %>% 
  mutate(CH01 = as.numeric(as.character(CH01))) %>%
   mutate(CH01_01 = as.numeric(as.character(CH01_01))) %>%
   mutate(CH01_02 = as.numeric(as.character(CH01_02))) %>%
   mutate(CH01_03 = as.numeric(as.character(CH01_03))) %>%
    mutate(CH01_04 = as.numeric(as.character(CH01_04))) %>%
  mutate(CH02 = as.numeric(as.character(CH02))) %>%
   mutate(CH02_01 = as.numeric(as.character(CH02_01))) %>%
   mutate(CH02_02 = as.numeric(as.character(CH02_02))) %>%
   mutate(CH02_03 = as.numeric(as.character(CH02_03))) %>%
    mutate(CH02_04 = as.numeric(as.character(CH02_04))) %>%
  mutate(CH03 = as.numeric(as.character(CH03))) %>%
mutate(MC01 = as.numeric(as.character(MC01))) %>%
   mutate(MC01_01 = as.numeric(as.character(MC01_01))) %>%
   mutate(MC01_02 = as.numeric(as.character(MC01_02))) %>%
   mutate(MC01_03 = as.numeric(as.character(MC01_03))) %>%
    mutate(MC01_04 = as.numeric(as.character(MC01_04))) %>%
  mutate(MC02 = as.numeric(as.character(MC02))) %>%
  mutate(MC03 = as.numeric(as.character(MC03))) %>%
  mutate(FINISHED = as.numeric(as.character(FINISHED))) %>%
  mutate(Q_VIEWER = as.numeric(as.character(Q_VIEWER))) %>% 
  mutate(LASTPAGE = as.numeric(as.character(LASTPAGE))) %>%
  mutate(MAXPAGE = as.numeric(as.character(MAXPAGE))) %>%
  mutate(DEG_TIME = as.numeric(as.character(DEG_TIME)))
}
```


## Check whether there are missing trials in the sosci and VOT files

```{r}
### Check whether there are missing trials
# VOT FILES
print('VOT files:')
for(i in 1:(length(vot_files_PWA)+length(vot_files_control))){
  if(i == 1){
    vot <- datafiles_vot[[i]]
  } else {
    vot <- rbind(vot, datafiles_vot[[i]])
  }
}

for(i in 1:length(unique(vot$subject))){
  for(j in 1:length(unique(vot$session))){
    for(k in 1:(nrow(vot[vot$subject == unique(vot$subject)[i] & 
                         vot$session == unique(vot$session)[j],])-1)){
      x1 <- vot$trial[vot$subject == unique(vot$subject)[i] & 
                        vot$session == unique(vot$session)[j]][k]
      x2 <- vot$trial[vot$subject == unique(vot$subject)[i] & 
                        vot$session == unique(vot$session)[j]][k+1]
      id <- vot$OR02_01[vot$subject == unique(vot$subject)[i] & 
                          vot$session == unique(vot$session)[j]][k]
      if(length(x1)== 0 | length(x1)==0){
        print(paste0('Trial number not recorded in subject ',
                     unique(vot$subject)[i], ' (', 
                     id, '), session ', unique(vot$session[j]), ' row ', k, 
                     ' or ', k+1, '.'))
      } else if (is.na(x1) | is.na(x2)){
        print(paste0('Trial number not recorded in subject ',
                     unique(vot$subject)[i], '(', 
                     id, '), session ',unique(vot$session[j]), ' row ', 
                     k, ' or ', k+1, '.'))
      } else if (x1 == x2) {
        print(paste0('Trial number not recorded in subject ',
                     unique(vot$subject)[i], ' (', id, '), session ', 
                     unique(vot$session[j]), ' row ', k, ' and ', k+1, 
                     '(trial number ', x1, ' and ', x2, ').'))
      } else if (x1 != x2-1) {
        print(paste0('Trial number missing between row ', k, ' and ', k+1, 
                     ' (trial numbers ', x1, ' and ', x2, ') in subject ',
                     unique(vot$subject)[i], ' (', id, '), session ',
                     unique(vot$session[j]), '.'))
      } else if (k == (nrow(vot[vot$subject == unique(vot$subject)[i] &
                                vot$session == unique(vot$session)[j],]))-1 & 
                 x2 != 164){
        print(paste0('Last trials are missing in subject ',
                     unique(vot$subject)[i], ' (', id, '), session ', 
                     unique(vot$session[j]), '(last trial numbers in row ', 
                     k, ' and ', k+1, ' are ', x1, ' and ', x2, ').'))
      }
    }
    }
  }

# SOSCI FILES - Need to be checked after cleaning
print('SoSci files:')
for(i in 1:(length(sosci_files_PWA)+length(sosci_files_control))){
  if(i == 1){
   sosci <- datafiles[[i]] %>% select(session, subject, trial,OR02_01)
  } else {
    sosci <- rbind(sosci, datafiles[[i]] %>% 
                     select(session, subject, trial, OR02_01))
  }
}

for(i in 1:length(unique(sosci$subject))){
  for(j in 1:length(unique(sosci$session))){
    for(k in 1:(nrow(sosci[sosci$subject == unique(sosci$subject)[i] &
                           sosci$session == unique(sosci$session)[j],])-1)){
      x1 <- sosci$trial[sosci$subject == unique(sosci$subject)[i] &
                          sosci$session == unique(sosci$session)[j]][k]
      x2 <- sosci$trial[sosci$subject == unique(sosci$subject)[i] &
                          sosci$session == unique(sosci$session)[j]][k+1]
      id <- sosci$OR02_01[sosci$subject == unique(sosci$subject)[i] &
                            sosci$session == unique(sosci$session)[j]][k]
      if(length(x1)== 0 | length(x1)==0){
        print(paste0('Trial number not recorded in subject ', unique(sosci$subject)[i], ' (', 
                     id, '), session ', unique(sosci$session[j]), ' row ', 
                     k, ' or ', k+1, '.'))
      } else if (is.na(x1) | is.na(x2)){
        print(paste0('Trial number not recorded in subject ',
                     unique(sosci$subject)[i], '(', 
                     id, '), session ',unique(sosci$session[j]), ' row ', 
                     k, ' or ', k+1, '.'))
      } else if (x1 == x2) {
        print(paste0('Trial number not recorded in subject ', unique(sosci$subject)[i], ' (', id, '), session ', 
                     unique(sosci$session[j]), ' row ', k, ' and ', 
                     k+1, '(trial number ', x1, ' and ', x2, ').'))
      } else if (x1 != x2-1) {
        print(paste0('Trial number missing between row ', k, ' and ', k+1, 
                     ' (trial numbers ', x1, ' and ', x2, ') in subject ',
                     unique(sosci$subject)[i], ' (', id, '), session ',
                     unique(sosci$session[j]), '.'))
      } else if (k == (nrow(sosci[sosci$subject == unique(sosci$subject)[i] &
                                  sosci$session ==
                                    unique(sosci$session)[j],]))-1 & 
                 x2 != 160){
        print(paste0('Last trials are missing in subject ',
                     unique(sosci$subject)[i], ' (', id, '), session ', 
                     unique(sosci$session[j]), '(last trial numbers in row ',
                     k, ' and ', k+1, ' are ', x1, ' and ', x2, ').'))
      }
    }
    }
  }
```

# Add array (actual stimuli in actual order) for each participant
For the spoken data, this is just to double check that everything went fine upon merging the files and to add the categories.

```{r add_arrays, warning = FALSE  }
# load arrays
arrays <- read.csv2(here::here("data", "supplementary_info", arrays), 
    sep = ";", na = "NA")

for (i in 1:(length(sosci_files_PWA)+length(sosci_files_control))) {
  x <- datafiles[[i]]
  ### Array column: OR02_01
  x$array <- as.numeric(as.character(x$OR01_01))
  
  ### Create a new dataframe with the fitting array
  for(j in 1:nlevels(as.factor(x$session))){
    eval(parse(text=paste0("y",j,"<- 
                           arrays[, unique(x$array[x$session == j])]")))
    
    ## Add stable columns
    eval(parse(text=paste0("y",j,"<- data.frame(
                           subject=rep(x$subject[x$session == j][1],
                           each=nrow(y", j,")),
                           session=rep(x$session[x$session == j][1],
                           each=nrow(y", j,")),
                           trial=rep(1:160),
                           item=y",j,")"
                           )))
    ## Add category and supercategory from the array 
    eval(parse(text=paste0("for (k in 1:nrow(y",j,")){
                           y", j,"$category[k] <- 
                              arrays$categorie[arrays$item == y",j,"$item[k]]; 
                           y", j,"$supercategory[k] <- 
                              arrays$supercategorie[arrays$item ==
                              y",j,"$item[k]];
                           }")))
    ## Add further stable columns
    for (m in 1:length(colnames(x[x$session == j,]))){
      if(colnames(x[x$session == j,])[m] != "subject" & 
         colnames(x[x$session == j,])[m] != "session" & 
         colnames(x[x$session == j,])[m] != "trial" & 
         colnames(x[x$session == j,])[m] != "audio") {
        if(length(unique(x[x$session == j,][m])) != 1){
          print(paste0('Error! Column ', colnames(x[x$session == j,])[m], 
                       ' is not stable'))
        } else{
              eval(parse(text=paste0("y",j,"<- data.frame(y",j,", ", 
              colnames(x[x$session == j,])[m], 
              "= rep(x[x$session==j,m][[1]][1], 
              each=nrow(y", j,")))")))
        } 
      }
    }

    ## Add unstable columns if there is info: AUDIO
    o <- 1
    eval(parse(text=paste0("for(n in 1:nrow(y",j,")){
    l <- strsplit(x$audio[x$session==j][o], '.',1);
    l <- tolower(l[[1]][1]);
    if(!is.na(l)){
    if(tolower(y", j,"$item[n]) == l){
      y",j,"$audio[n] <- x$audio[x$session==j][o];
      o <- o+1
    }} else {
      y",j,"$audio[n] <- NA;
      if(is.na(l)){
      o <- o+1
      }
    }}")))
  }
  y <- rbind(y1,y2,y3)
  datafiles[[i]] <- y
}
```

Check that everything went fine

```{r}
for(i in 1:length(datafiles)){
  x <- as.data.frame(datafiles[[i]])
  for(j in 1:nrow(x)){
      y <- x$audio[j]
        if(tolower(strsplit(y, ".", fixed=TRUE)[[1]][1]) != x$item[j] |
           is.na(y)){
          print(paste0('Audiofiles and Items dont fit in subject ', 
                       x$subject[1], ', session ', x$session[j], ', 
                       trial ', x$trial[j], '. The audiofilename is ', 
                       x$audio[j], ', but the item should be ', 
                       x$item[j], '.'))
        }
  }
}
```

There are four trials with missing data -> Technical errors!


# Bind the dataframes together

```{r bind_input_dataframes_into_one}
df <- bind_rows(datafiles)

# Check whether the expected file length fits the actual file length
nrow(df) == 2*20*3*160
```

# Combine data frame with audio files

```{r}
# Bind VOT files into one
for(i in 1:length(datafiles_vot)) {
  datafiles_vot[[i]]$error <- as.character(datafiles_vot[[i]]$error)
  datafiles_vot[[i]]$correct <- as.character(datafiles_vot[[i]]$correct)
}
vot <- bind_rows(datafiles_vot)

vot %>% group_by(subject, session) %>% count()

# delete practice trials (4 per subject)
sum(stringr::str_detect(vot$File_name, "PA0"), na.rm=T) == 2*20*3*4
vot %>% filter(!stringr::str_detect(vot$File_name, "PA0")) -> vot

# fix participant ID
for(i in 1:nrow(vot)){
  x <- strsplit(vot$name[i], ".", fixed=TRUE)
  x <- strsplit(x[[1]][2], "/", fixed=TRUE) 
  x <- stringr::str_sub(x[[1]][2], 1,6)
  vot$OR02_01[i] <- toupper(x)
}
df <- df %>% mutate(OR02_01 = toupper(OR02_01))
# Have both data frames the same participant ID? 
unique(df$OR02_01) %in% unique(vot$OR02_01)
unique(vot$OR02_01) %in% unique(df$OR02_01)

# Fix file name ending in both data frames
df %>% mutate(audio2=case_when(endsWith(audio, ".webm") ~ 
                                 stringr::str_sub(audio, 1, -18),
                               endsWith(audio, ".ogg") ~
                                 stringr::str_sub(audio, 1, -17))) -> df
vot$File_name2 <- stringr::str_sub(vot$File_name, 1, -17)

# Fix Umlaute
vot$File_name2[vot$File_name2 == "Loewenzahn"] <- "Löwenzahn"
vot$File_name2[vot$File_name2 == "Lˆwenzahn"] <- "Löwenzahn"
vot$File_name2[vot$File_name2 == "Wuerfel"] <- "Würfel"
vot$File_name2[vot$File_name2 == "Muelleimer"] <- "Mülleimer"
vot$File_name2[vot$File_name2 == "Buerste"] <- "Bürste"
vot$File_name2[vot$File_name2 == "Saege"] <- "Säge"
vot$File_name2[vot$File_name2 == "Schluessel"] <- "Schlüssel" 
vot$File_name2[vot$File_name2 == "Kopfhoerer"] <- "Kopfhörer"
vot$File_name2[vot$File_name2 == "Geschirrspueler"] <- "Geschirrspüler"
vot$File_name2[vot$File_name2 == "UBoot"] <- "U-Boot"
vot$File_name2[vot$File_name2 == "Kuehlschrank"] <- "Kühlschrank"
vot$File_name2[vot$File_name2 == "Kaefig"] <- "Käfig" 
vot$File_name2[vot$File_name2 == "Marienkaefer"] <- "Marienkäfer"
vot$File_name2[vot$File_name2 == "Marienk‰fer"] <- "Marienkäfer"
vot$File_name2[vot$File_name2 == "Marienk‰fer"] <- "Marienkäfer"
vot$File_name2[vot$File_name2 == "Loewe"] <- "Löwe" 
vot$File_name2[vot$File_name2 == "Loeffel"] <- "Löffel"  
vot$File_name2[vot$File_name2 == "Faecher"] <-  "Fächer"
vot$File_name2[vot$File_name2 == "F‰cher"] <-  "Fächer"
vot$File_name2[vot$File_name2 == "F‰cher"] <-  "Fächer"
vot$File_name2[vot$File_name2 == "Baer"] <- "Bär"  

# Write VOT data into df
df$File_name <- NA
df$VOT<- NA
df$correct <- NA
df$AR <- NA
df$error <- NA
df$name <- NA
for(i in 1:nrow(vot)){
  df$File_name[df$OR02_01 == vot$OR02_01[i] & df$session == vot$session[i] & 
           df$audio2 == vot$File_name2[i]] <- vot$File_name2[i]
  df$VOT[df$OR02_01 == vot$OR02_01[i] & df$session == vot$session[i] & 
           df$audio2 == vot$File_name2[i]] <- vot$VOT[i]
  df$correct[df$OR02_01 == vot$OR02_01[i] & df$session == vot$session[i] & 
           df$audio2 == vot$File_name2[i]] <- vot$correct[i]
  df$AR[df$OR02_01 == vot$OR02_01[i] & df$session == vot$session[i] & 
           df$audio2 == vot$File_name2[i]] <- vot$AR[i]
  df$error[df$OR02_01 == vot$OR02_01[i] & df$session == vot$session[i] & 
           df$audio2 == vot$File_name2[i]] <- vot$error[i]
   df$name[df$OR02_01 == vot$OR02_01[i] & df$session == vot$session[i] & 
           df$audio2 == vot$File_name2[i]] <- vot$name[i]
}


# Check whether merging worked properly
sum(!is.na(df$File_name)) == nrow(vot) 
  # all file names were transmitted to the big df
x <- df %>% filter(is.na(File_name)) 
  # four files are missing = technical errors
(x %>% select(subject, session, trial, item, audio, File_name) -> x)
table(df$audio[is.na(df$File_name)])
```



# Roughly check participants' adherence to the experiment
**Did all participants finish the experiment?**

```{r prolific_check}
# did all participants finish the experiment?
for(i in 1:length(unique(df$subject))) {
  if(all(df$FINISHED[df$subject==unique(df$subject[i])] != 0) |
     all(df$LASTPAGE[df$subject==unique(df$subject[i])] != 32)){
      print(paste(i,":"))
  print("Experiment completed?")
  print(table(df$FINISHED[df$subject==unique(df$subject[i])])/160)
  print("What was the last experimental page reached?")
  print(table(df$LASTPAGE[df$subject==unique(df$subject[i])])/160)
  }
}
```

Make sure patient and control group matching worked fine

```{r}
overview <- data.frame(PWA=unique(df$subject)[unique(df$subject)<200], 
           PWA_codes=unique(df$OR02_01[df$subject < 200]), 
           control=unique(df$subject)[unique(df$subject)>200],
           control_codes=unique(df$OR02_01[df$subject>200]))
# make sure the extraction worked
for(i in 1:nrow(overview)){
  if(all(df$OR02_01[df$subject==overview$PWA[i]] != overview$PWA_code[i])){
    print('error PWA')
  }
  if(all(df$OR02_01[df$subject==overview$control[i]] != overview$control_code[i])){
    print('error control')
  }
}
# add age and gender
for(i in 1:nrow(overview)){
  overview$PWA_gender[i] <- df$gender[df$subject == overview$PWA[i]][1]
  overview$control_gender[i] <- df$gender[df$subject == overview$control[i]][1]
  overview$PWA_age[i] <- df$age[df$subject == overview$PWA[i]][1]
  overview$control_age[i] <- df$age[df$subject == overview$control[i]][1]
}

# export
write.csv(df, here::here("data", "transient_data_files",
                         "matching_overview.csv"), 
            row.names = FALSE)
```

# Double-check time taken

```{r}
range(as.numeric(as.character(df$TIME003))) # welcome page
range(as.numeric(as.character(df$TIME004))) # consent
range(as.numeric(as.character(df$TIME005))) # demographics
range(as.numeric(as.character(df$TIME006))) # general instructions
range(as.numeric(as.character(df$TIME007)), na.rm=T) # array loading (not visible for participant)
range(as.numeric(as.character(df$TIME008))) # familiarization instructions
range(as.numeric(as.character(df$TIME009)), na.rm=T) # familiarization

# Some participants already open the link prior to the experiment. Therefore, well only consider the time starting from the demographics page
for(i in 1:nrow(df)){
  df$time_correct[i] <- sum(df[i,] %>% 
        select(starts_with("TIME")), na.rm=T)/60
}

# Get an overview
df %>% group_by(subject, session) %>% count(time_correct)
df %>% 
  summarise(m = mean(time_correct),
                 sd = sd(time_correct), 
                 min = min(time_correct),
                 max = max(time_correct))
df %>% group_by(type) %>% 
  summarise(m = mean(time_correct),
                 sd = sd(time_correct), 
                 min = min(time_correct),
                 max = max(time_correct))
df %>% group_by(type, session) %>% 
  summarise(m = mean(time_correct),
                 sd = sd(time_correct), 
                 min = min(time_correct),
                 max = max(time_correct))
```

# Calculate mean semantic similarity per group 

```{r}
### Semantic similarity
# install.packages("LSAfun")
# install.packages("Rmisc")
# install.packages("tidyverse")
# install.packages("here")
# install.packages("cowplot")
library(LSAfun)

##  load dewak dataframe
load(here::here("data", "dewak",
  "dewak100k_lsa.rda"))


## Within each category, calculate pairwise semantic similarity and calculate mean and sd
df %>% group_by(category, item) %>% count() %>%
  select(category, item) -> stims
stims$min_cat <- NA
stims$max_cat <- NA
stims$mean_cat <- NA
stims$sd_cat <- NA
vectors <- data.frame(category=NA, stims1=NA, stims2=NA)
for(i in 1:length(unique(df$category))){
  subset <- stims %>% filter(category==unique(df$category)[i])
  subset2 <- rbind(subset[1,], subset[1,], subset[1,], subset[1,],
                  subset[2,], subset[2,], subset[2,],
                  subset[3,], subset[3,],
                  subset[4,])
  subset2$item2 <- c(subset$item[2], subset$item[3], subset$item[4], subset$item[5],
                     subset$item[3], subset$item[4], subset$item[5],
                     subset$item[4], subset$item[5],
                     subset$item[5])
  for(j in 1:nrow(subset2)){
      subset2$cosine[j] <- 
    LSAfun::pairwise(subset2$item[j], subset2$item2[j],tvectors = dewak100k_lsa)
  }
  min <- min(subset2$cosine)
  max <- 
  mean <- mean(subset2$cosine)
  sd <- sd(subset2$cosine)
  stims$min_cat[stims$category==unique(df$category)[i]] <- min(subset2$cosine, na.rm=T)
  stims$max_cat[stims$category==unique(df$category)[i]] <- max(subset2$cosine, na.rm=T)
  stims$mean_cat[stims$category==unique(df$category)[i]] <- mean(subset2$cosine, na.rm=T)
  stims$sd_cat[stims$category==unique(df$category)[i]] <- sd(subset2$cosine, na.rm=T) 
}

stims %>% group_by(category,mean_cat, sd_cat, min_cat, max_cat) %>% count()

# Average semantic similarity in experimental categories
paste0('Mean semantic similarity per category: ', 
       round(mean(stims$mean_cat[stims$category != "Filler"], na.rm=T),3), " SD: ",
       round(mean(stims$sd_cat[stims$category != "Filler"], na.rm=T), 3), 
       " (caution: Some stimuli are not in the dewak database)")

# Average semantic similarity in fillers
paste0('Mean semantic similarity across fillers: ', 
       round(mean(stims$mean_cat[stims$category == "Filler"], na.rm=T),3), " SD: ",
       round(mean(stims$sd_cat[stims$category == "Filler"], na.rm=T), 3), 
       " (caution: Some stimuli are not in the dewak database)")
```


# Export prepared data frame
Anonymize data frame

```{r}
df <- df %>% select(-c("QUESTNNR", "STARTED", "OR01_01")) %>% #, "OR02_01")) %>%
  # drop unnecessary columns
  select(-c("os_system", "SD22_BID", "browser_automatic",
            "system_format", "screen_width", "screen_height",
            "questionnaire_width", starts_with("TIME0"), 
            "FINISHED", "Q_VIEWER", 
            "LASTPAGE", "MAXPAGE", "DEG_TIME"))
                
```

Reduce data frame to relevant columns

```{r}
# head(df)
df %>% select(type, subject, session, trial, item, category, supercategory, 
              VOT, correct, AR, error, gender, age,language, handedness, 
              starts_with("CH"), array, comments, timetotal, time_correct,
              OR02_01) -> d
```

```{r export_data}
write.csv(d, here::here("data", "transient_data_files", output), 
            row.names = FALSE)
write.csv(df, here::here("data", "transient_data_files",
                         "aphasia_final_complete.csv"), 
            row.names = FALSE)
```
