---
title: '04 CSI online aphasia: Spoken - Descriptives'
author: "Kirsten Stark"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load packages

```{r load_packages}
library(dplyr)
library(tidyr)

rm(list = ls())
```


## Load and preprocess data

```{r load_data}
options( "encoding" = "UTF-8" )

# input
input <- "aphasia_patient_TeaP.csv"

# load data
df <- read.csv(here::here("data", "transient_data_files", input), sep = ",",  na = "")
```

## Duration of the experiment

```{r duration}
print("Total duration, not outlier corrected")
mean(df$timetotal, na.rm=TRUE) # 36,27 min
sd(df$timetotal)
range(df$timetotal) # 19 to 126 min

print("Total duration, split by session")

df %>% group_by(session) %>% summarise(mean = mean(timetotal),
                                       sd = sd(timetotal), 
                                       min = min(timetotal), 
                                       max = max(timetotal))
```


## Description of participants

Gender: 

```{r gender}
df <- df %>% mutate(gender_char = case_when(gender == 1 ~ "female", 
                                     gender == 2 ~ "male"))
table(df$gender_char)/160 # 1 = female, 2 = male, 3 = diverse

print("percentage female:")
sum(df$gender == 1)/nrow(df)
```

Age: 

```{r age}
print("mean:"); mean(df$age)
print("sd:"); sd(df$age)
print("range:"); range(df$age)
```

Handedness: 

```{r handedness}
# 1 = left handed, 2 = right handed, 3 = ambidexter/both
df <- df %>% mutate(handedness_char = case_when(handedness == 1 ~ "left-handed", 
                                     handedness == 2 ~ "right-handed"))
table(df$handedness_char)/160 

print("percentage right-handed:")
sum(df$handedness == 2)/nrow(df)
```


Mother tongue (experiment was restricted to native German speakers): This seems to have worked

```{r}
table(df$language) # 1 = yes (mother tongue is German), 2 = no
table(df$language.test) # 1 = der, 2 = die, 3 = das (das is correct)
```



## Attention checks
*1) Item vs. non-item*

```{r item vs non-item}
## Item vs. non-item
# CH01_01 (Taube), CH01_02 (Apfel), CH02_01 (Luftballon) and CH02_02 (Biene) are items and 2 should be selected,
# CH02_03 (Radio), CH02_04 (Sparschwein), CH02_03 (Laptop) and CH02_04 (Wattestäbchen) are non-items and 1 should be selected
## Did participants cheat
# CH03 = 1 - yes, I worked through it till the end,
# CH03 = 2 - no, I stopped or cheated midway
# CH03 = -9 - no answer

attcheck <- data.frame(subject = unique(df$subject)) 

df <- df %>% mutate(itemvsnonitem1 = 
                      case_when(CH01_01==2 & CH01_02==2 & CH01_03==1 & CH01_04==1 ~2,
                                CH01_01==2 || CH01_02==2 ~1, 
                                CH01_01!=2 & CH01_02!=2 ~0)) %>%
  mutate(itemvsnonitem2 = 
                      case_when(CH02_01==2 & CH02_02==2 & CH02_03==1 & CH02_04==1 ~2,
                                CH02_01==2 || CH02_02==2 ~1, 
                                CH02_01!=2 & CH02_02!=2 ~0))
table(df$itemvsnonitem1)/160
table(df$itemvsnonitem2)/160

# attcheck <- data.frame(subject = unique(df$subject))
# 
# 
# data <- data %>% mutate(attcheck =
#                   ifelse(CH01_01 == 2 & CH01_02 == 2 & CH02_01 == 2 & CH02_02 == 2 &
#                   CH01_03 == 1 & CH01_04 == 1 & CH02_03 == 1 & CH02_04 == 1, 1, 0)) %>%
#                    mutate(cheat = ifelse(CH03 == 1,1,ifelse(CH03 == 2,2,0)))
# data.frame(data$subject, )
# table(data$attcheck)
# table(data$cheat)
# 
# # get prolific IDs of participants who failed the attention check
# #pretest %>% subset(attcheck == 0 & cheat == 2 ) %>%
# #  pull(SD24_01) # SD24_01 is prolific ID
# 
# # subset to participants who passed only
# valid <- pretest  %>% filter(attcheck == 1 & cheat != 2)
# 
# inspect <- data.frame(df$subject, df$word, df$fam_typed)

```


*2) Cheating*

```{r cheating}
df <- df %>% mutate(CH03 = case_when(CH03 == 1 ~ 
                                       " Ja, ich habe alles bis zum Ende bearbeitet.",
                                             CH03 == 2 ~ 
                                       "Nein, ich habe zwischendurch aufgehoert oder geschummelt."))
table(df$CH03)/160
```

## Comments
Comments don't indicate any problems that should lead to participant exclusion: 

```{r comments}
table(df$comments)/160
```



## Fully anonymize data and reduce data frame

```{r anonymize}
df_a <- df %>% dplyr::select(!"gender" & !starts_with("language") & 
                               !starts_with("TIME") & 
                               !starts_with("handedness") &
                               !starts_with("fingers") &
                               !starts_with("browser") & 
                               !starts_with("operator_system") &
                               !starts_with("system") &
                                !starts_with("KB") &
                               !starts_with("CH0") & !starts_with("X.") &
                               !starts_with("screen") & !starts_with("os") &
                               !starts_with("questionnaire") & !"OR01_01" & 
                               !"comments" & 
                               !"FINISHED" & !"Q_VIEWER" & 
                               !"LASTPAGE" & !"MAXPAGE" & 
                               !"DEG_TIME"& !"type" &  
                               !"gender_char" & !"itemvsnonitem1" &
                               !"itemvsnonitem2" & 
                               !"QUESTNNR" & !"STARTED" & !"OR02_01" & 
                                !"SD22_BID" & !starts_with("MC") &
                                !"audio"& !"name" & !"audio_vot")
```


```{r write_anonymized_df}
write.csv(df_a, here::here("data","data_long_anonymous.csv"))
```


