---
title: '03 CSI online aphasia: Spoken - Descriptives'
author: "Kirsten Stark"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load packages

```{r load_packages}
library(dplyr)
library(tidyr)

rm(list = ls())
```


## Load and preprocess data

```{r load_data}
options( "encoding" = "UTF-8" )

# input
input <- "aphasia_final.csv"

# load data
df <- read.csv(here::here("data", "transient_data_files", input), 
               sep = ",",  na = "")
```

## Duration of the experiment

```{r duration}
print("Total duration, not outlier corrected")
# mean(df$timetotal, na.rm=TRUE) # 33.13 min
mean(df$time_correct)
sd(df$timetotal) # 21.04 min
range(df$timetotal) # 15 to 126 min

print("Total duration, split by session")

df %>% group_by(type,session) %>% summarise(mean = mean(timetotal),
                                            median=median(timetotal),
                                       sd = sd(timetotal), 
                                       min = min(timetotal), 
                                       max = max(timetotal))
```


## Description of participants

Gender: 

```{r gender}
(df %>% mutate(gender_char = case_when(gender == 1 ~ "female", 
                                     gender == 2 ~ "male")) %>% 
  group_by(type, gender_char) %>% count(gender_char) %>% 
   mutate(n=n/160/3) -> gender)
 # 1 = female, 2 = male, 3 = diverse

print("percentage female:")
sum(df$gender == 1)/nrow(df)
```

Age: 

```{r age}
print('age:')
df %>% group_by(type) %>% 
  summarise(mean=round(mean(age),2), sd=round(sd(age),2), min=min(age), max=max(age))
```

Handedness: 

```{r handedness}
# 1 = left handed, 2 = right handed, 3 = ambidexter/both
(handedness <- df %>% mutate(handedness_char = case_when(handedness == 1 ~ "left-handed", 
                                     handedness == 2 ~ "right-handed", 
                                     handedness==3 ~ "ambidexter/both")) %>% 
  group_by(type) %>% count(handedness_char))

print("percentage right-handed:")
print('PWA')
sum(df$handedness[df$type=="PWA"] == 2)/nrow(df[df$type=="PWA",])
print('control')
sum(df$handedness[df$type=="control"] == 2)/nrow(df[df$type=="control",])
```


Mother tongue (experiment was restricted to native German speakers): This seems to have worked

```{r}
table(df$language) # 1 = yes (mother tongue is German), 2 = no
```



## Attention checks
*1) Item vs. non-item*

```{r item vs non-item}
## Item vs. non-item
# CH01_01 (Taube), CH01_02 (Apfel), CH02_01 (Luftballon) and CH02_02 (Biene) are items and 2 should be selected,
# CH01_03 (Radio), CH01_04 (Sparschwein), CH02_03 (Laptop) and CH02_04 (Wattestäbchen) are non-items and 1 should not be selected
## Did participants cheat
# CH03 = 1 - yes, I worked through it till the end,
# CH03 = 2 - no, I stopped or cheated midway
# CH03 = -9 - no answer

attcheck <- data.frame(subject = unique(df$subject)) 

df <- df %>% mutate(itemvsnonitem1 = 
    case_when(CH01_01==2 & CH01_02==2 & CH01_03==1 & CH01_04==1 ~2, # all correct
              CH01_01==2 | CH01_02==2 ~1, # one correct
              CH01_01!=2 & CH01_02!=2 ~0)) %>% # none correct
  dplyr::mutate(itemvsnonitem2 = 
    case_when(CH02_01==2 & CH02_02==2 & CH02_03==1 & CH02_04==1 ~2,
              CH02_01==2 | CH02_02==2 ~1, 
              CH02_01!=2 & CH02_02!=2 ~0))
df %>% group_by(type, session) %>% count(itemvsnonitem1) %>% mutate(n=n/160)
df %>% group_by(type, session) %>% count(itemvsnonitem2) %>% mutate(n=n/160)
# table(df$itemvsnonitem1)/160
# table(df$itemvsnonitem2)/160

```

All had at leas one item selected correctly in the attention test

*2) Cheating*

```{r cheating}
df <- df %>% mutate(CH03 = case_when(CH03 == 1 ~ 
                                       " Ja, ich habe alles bis zum Ende bearbeitet.",
                                             CH03 == 2 ~ 
                                       "Nein, ich habe zwischendurch aufgehoert oder geschummelt."))
df %>% group_by(type, session) %>% count(CH03) %>% mutate(n=n/160)
table(df$CH03)/160
```

## Comments
Comments don't indicate any problems that should lead to participant exclusion: 

```{r comments}
table(df$comments)/160
```

## Arrays

```{r}
table(df$array)/160
x <- df %>% group_by(subject, session) %>% count(array) %>% mutate(n=n/160)
array_rep = 0
for(i in 2:nrow(x)){
  if(x$subject[i-1] == x$subject[i] & x$array[i-1] == x$array[i]){
    array_rep = array_rep+1
  }
}
print(paste0(array_rep, " time an array was repeated within the same participant")) 

df %>% group_by(type, session) %>% count(array) %>% mutate(n=n/160) %>% arrange(array)
df %>% count(array) %>% mutate(n=n/160)
```

## Fully anonymize data and reduce data frame

```{r anonymize}
# df_a <- df %>% dplyr::select(!"gender" & !starts_with("language") & 
#                                !starts_with("handedness") &
#                                !starts_with("fingers") & 
#                                 !starts_with("KB") &
#                                !starts_with("CH0") & 
#                                !"comments" & !"type" &  
#                                !"gender_char" & !"itemvsnonitem1" &
#                                !"itemvsnonitem2" &  
#                                !starts_with("MC") &
#                                 !"name" & !"time_wo_outlier" )
```


```{r write_anonymized_df}
# write.csv(df_a, here::here("data","data_long_anonymous.csv"))
```
